Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-26 code-tests.tex
one additional update of ZP test

Figure~\ref{fig.pancake} shows the key features of this test problem.
The strong shocks and large density gradients are well-resolved, with
density and velocity jumps being well-delineated.  The key features of
this test problem can be resolved with far fewer cells -- simulations
including a mere 8 cells resolve the key features, as shown in
sections 3.3-3.5 of~\citet{1996PhDT........80B} -- but we choose a
higher resolution here for illustrative purposes.

>>>>

Figure~\ref{fig.pancake} shows the key features of this test problem.
The strong shocks and large density gradients are well-resolved, with
density and velocity jumps being well-delineated.  The key features of
this test problem can be resolved with far fewer cells -- simulations
including a mere 8 cells resolve the key features, as shown in
sections 3.3.4-3.3.5 of~\citet{1996PhDT........80B} -- but we choose a
higher resolution here for illustrative purposes.
